---
title: "GCI-Go reaches the Cloud: 2 Intances"
author: "Daniel Fireman (danielfireman@gmail.com)"
date: "January, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(resample)
require(dplyr)
require(stringr)
require(cowplot)

EXPERIMENT_DURATION <- 80000 # 80s
```
# Experiment setup

* Experiment duration: 80secs (results ignored the first and last 10 seconds)
* Number of experiment repetitions: 5
* Throughput: 3000 reqs/sec
* Number of buffered messages: 5000 (this will result in a ~2GB heap usage)
* Message size: 300KB
* Go: 1.8
* Number of instances: 2
* Servers: 2 vCPUs, 4GB RAM

# Latency

Latency was measured at the load balancer (NGINX).

```{r accesslog.func}
read.accesslog <- function(f) {
  # https://lincolnloop.com/blog/tracking-application-response-time-nginx/
  al <- read.csv(f, sep=";", colClasses=c("upstream_response_time"="character"))
  # request processing time in seconds with a milliseconds resolution;
  # time elapsed between the first bytes were read from the client and
  # the log write after the last bytes were sent to the client
  # http://nginx.org/en/docs/http/ngx_http_log_module.html.
  al$request_time <- al$request_time * 1000 # Making it milliseconds.
  # Calculating elapsed time. It is more useful than timestamp.
  al <- al %>% arrange(timestamp)
  al$exp_dur_ms <- c(0, al$timestamp[2:NROW(al)]-al$timestamp[1]) * 1000
  al$hop1 <- sub(',.*$', '', al$upstream_response_time)
  al$hop1 <- as.numeric(al$hop1)*1000
  al$hop2 <- sub('^.*,', '', al$upstream_response_time)
  al$hop2 <- as.numeric(al$hop2)*1000
  al$num_hops <- str_count(al$upstream_response_time, ',')+1
  # Removing the first and last 10 seconds from the experiment results.
  return(filter(al, exp_dur_ms > 10000 & exp_dur_ms < (EXPERIMENT_DURATION-10000)))
}
```

```{r al_3K_300KB_5K, echo=F, warning=F}
al.gci <- rbind(
  read.accesslog("/tmp/2instances/nginx_access_gci_3K_300KB_5K_1.log"),
  read.accesslog("/tmp/2instances/nginx_access_gci_3K_300KB_5K_2.log"),
  read.accesslog("/tmp/2instances/nginx_access_gci_3K_300KB_5K_3.log"),
  read.accesslog("/tmp/2instances/nginx_access_gci_3K_300KB_5K_4.log"),
  read.accesslog("/tmp/2instances/nginx_access_gci_3K_300KB_5K_5.log"))


al.nogci <- rbind(
  read.accesslog("/tmp/2instances/nginx_access_nogci_3K_300KB_5K_1.log"),
  read.accesslog("/tmp/2instances/nginx_access_nogci_3K_300KB_5K_2.log"),
  read.accesslog("/tmp/2instances/nginx_access_nogci_3K_300KB_5K_3.log"),
  read.accesslog("/tmp/2instances/nginx_access_nogci_3K_300KB_5K_4.log"),
  read.accesslog("/tmp/2instances/nginx_access_nogci_3K_300KB_5K_5.log"))
```
## Overall Summary

```{r}
print(paste("Number of requests considered (GCI On): ", NROW(al.gci)))
summary(al.gci$request_time)
print(paste("Number of requests considered (GCI Off): ", NROW(al.nogci)))
summary(al.nogci$request_time)
hist(log(al.gci$request_time), breaks=50, main="Overall Latency (GCI ON)", ylab = "Frequency", xlab="Latency in log scale (ms)", xlim=c(0,7))
hist(log(al.nogci$request_time), breaks=50, main="Overall Latency (GCI OFF)",ylab = "Frequency", xlab="Latency in log scale (ms)", xlim=c(0,7))
quantile(al.gci$request_time, c(0.9,0.99,0.999,0.9999, 0.99999))
quantile(al.nogci$request_time, c(0.9,0.99,0.999,0.9999, 0.99999))
```

## Null-Hypothesis check (around the median)

```{r}
# Non parametric test which checks the pseudo-median
# https://en.wikipedia.org/wiki/Mann%E2%80%93Whitney_U_test
wilcox.test(sample(al.gci$request_time, 50000), conf.int = TRUE, conf.level = 0.95)
wilcox.test(sample(al.nogci$request_time, 50000), conf.int = TRUE, conf.level = 0.95)
```

# Failed Requests
```{r}
failed.requests <- filter(al.gci, status != 200)
print(paste("Number of failed requests: ", NROW(failed.requests)))
summary(failed.requests$request_time)
```
## Requests that have not been shed

```{r direct_requests}
direct.requests <- filter(al.gci, num_hops==1)
print(paste("Number of requests that have not been shed: ", NROW(direct.requests), "(", (NROW(direct.requests)/NROW(al.gci))*100,"%)"))
summary(direct.requests$request_time)
hist(direct.requests$request_time, breaks=50, main="Latency of requests that have not been shed", xlab="Latency (ms)")
quantile(direct.requests$request_time, c(0.9,0.99,0.999,0.9999, 0.99999))
```

## Shed requests

The requests have been shed by the first upstream service and processed by the second.

### Overall Stats

```{r resent_requests}
resent.requests <- filter(al.gci, num_hops > 1)
print(paste("Number of shed requests: ", NROW(resent.requests), "(", (NROW(resent.requests)/NROW(al.gci))*100,"%)"))
summary(resent.requests$request_time)
hist(resent.requests$request_time, breaks=50, main="Latency of requests that have been shed", xlab="Latency (ms)")
quantile(resent.requests$request_time, c(0.9,0.99,0.999,0.9999, 0.99999))
```
### First node stats

Statistics about the time for a request to reach the first instance (upstream
server), go over the queue and be shed.

```{r resent_requests_hop1}
summary(resent.requests$hop1)
hist(resent.requests$hop1, main="Latency of the first upstream service (shed)", xlab="Latency (ms)")
quantile(resent.requests$hop1, c(0.9,0.99,0.999,0.9999, 0.99999))
```

### Processing instance stats

After being shed by the first instance the request is redirected. The following
statistic represents the latency considering only of the second upstream server.

```{r resent_requests_hop2}
summary(resent.requests$hop2)
hist(resent.requests$hop2, main="Latency of the second upstream service (shed)", xlab="Latency (ms)")
quantile(resent.requests$hop2, c(0.9,0.99,0.999,0.9999, 0.99999))
```

# Garbage Collector

```{r gctrace.func}
# Parsing some of gctrace fields and doing some cleanup.
read.gctrace <- function(f) {
  df <- read.csv(f, sep = " ", colClasses=c("wallclock"="character", "mem"="character"))
  df$walltime <-sapply(strsplit(df$wallclock, split="+", fixed=T) , function (x) sum(as.numeric(unlist(x))))
  df$time <- as.numeric(gsub("@|s","", df$time))*1000 # Making it elaspsed time in ms.
  df$isforced <- ifelse(is.na(df$isforced),0,df$isforced)
  df$cleaned <-sapply(strsplit(df$mem, split="->", fixed=T), function (x) as.numeric(x[1])-as.numeric(x[3]))
  # Removing the first and last 10 seconds from the experiment results.
  df <- filter(df, time > 10000  & time < (EXPERIMENT_DURATION-10000))
  return(na.omit(df))
}
```
```{r gctrace, echo=F}
gctrace.gci <- rbind(
  read.gctrace("/tmp/2instances/gctrace_gci_3K_300KB_5K_0_1.out"),
  read.gctrace("/tmp/2instances/gctrace_gci_3K_300KB_5K_1_1.out"),
  read.gctrace("/tmp/2instances/gctrace_gci_3K_300KB_5K_0_2.out"),
  read.gctrace("/tmp/2instances/gctrace_gci_3K_300KB_5K_1_2.out"),
  read.gctrace("/tmp/2instances/gctrace_gci_3K_300KB_5K_0_3.out"),
  read.gctrace("/tmp/2instances/gctrace_gci_3K_300KB_5K_1_3.out"),
  read.gctrace("/tmp/2instances/gctrace_gci_3K_300KB_5K_0_4.out"),
  read.gctrace("/tmp/2instances/gctrace_gci_3K_300KB_5K_1_4.out"),
  read.gctrace("/tmp/2instances/gctrace_gci_3K_300KB_5K_0_5.out"),
  read.gctrace("/tmp/2instances/gctrace_gci_3K_300KB_5K_1_5.out")
)
gctrace.nogci <- rbind(
  read.gctrace("/tmp/2instances/gctrace_nogci_3K_300KB_5K_0_1.out"),
  read.gctrace("/tmp/2instances/gctrace_nogci_3K_300KB_5K_1_1.out"),
  read.gctrace("/tmp/2instances/gctrace_nogci_3K_300KB_5K_0_2.out"),
  read.gctrace("/tmp/2instances/gctrace_nogci_3K_300KB_5K_1_2.out"),
  read.gctrace("/tmp/2instances/gctrace_nogci_3K_300KB_5K_0_3.out"),
  read.gctrace("/tmp/2instances/gctrace_nogci_3K_300KB_5K_1_3.out"),
  read.gctrace("/tmp/2instances/gctrace_nogci_3K_300KB_5K_0_4.out"),
  read.gctrace("/tmp/2instances/gctrace_nogci_3K_300KB_5K_1_4.out"),
  read.gctrace("/tmp/2instances/gctrace_nogci_3K_300KB_5K_0_5.out"),
  read.gctrace("/tmp/2instances/gctrace_nogci_3K_300KB_5K_1_5.out")
)
```

## Overall Stats

```{r gctrace.overall}
print(paste("Total number of collections considered (GCI On):", NROW(gctrace.gci)))
summary(gctrace.gci$walltime)
print(paste("Total number of collections considered (GCI Off):", NROW(gctrace.nogci)))
summary(gctrace.nogci$walltime)
hist(gctrace.gci$walltime, breaks=50, main="Garbage Collection Duration (GCI On)", xlab="GC Duration - Wall time (ms)", ylab="Frequency")
hist(gctrace.nogci$walltime, breaks=50, main="Garbage Collection Duration (GCI Off)", xlab="GC Duration - Wall time (ms)", ylab="Frequency")
quantile(gctrace.gci$walltime, c(0.9,0.99,0.999,0.9999, 0.99999))
quantile(gctrace.nogci$walltime, c(0.9,0.99,0.999,0.9999, 0.99999))
```

## Number of MBs cleaned by GC
```{r gctrace.cleaned}
summary(gctrace.gci$cleaned)
summary(gctrace.nogci$cleaned)
hist(gctrace.gci$cleaned, breaks=50, main="Amount of garbage cleaned at each collection (GCI On)", xlab="Amount of garbage cleaned (MB)")
hist(gctrace.nogci$cleaned, breaks=50, main="Amount of garbage cleaned at each collection (GCI Off)", xlab="Amount of garbage cleaned (MB)")
quantile(gctrace.gci$cleaned, c(0.9,0.99,0.999,0.9999, 0.99999))
quantile(gctrace.nogci$cleaned, c(0.9,0.99,0.999,0.9999, 0.99999))
```

# CPU Usage

```{r cpu.func} 
read.cpu <- function(f) {
  df <- read.csv(f)
  return(na.omit(df[11:NROW(df-10),]))
}
```

```{r cpu_overall, echo=F, warning=F}
cpu.gci <- rbind(
  read.cpu("/tmp/2instances/cpu_gci_3K_300KB_5K_0_1.csv"),
  read.cpu("/tmp/2instances/cpu_gci_3K_300KB_5K_1_1.csv"),
  read.cpu("/tmp/2instances/cpu_gci_3K_300KB_5K_0_2.csv"),
  read.cpu("/tmp/2instances/cpu_gci_3K_300KB_5K_1_2.csv"),
  read.cpu("/tmp/2instances/cpu_gci_3K_300KB_5K_0_3.csv"),
  read.cpu("/tmp/2instances/cpu_gci_3K_300KB_5K_1_3.csv"),
  read.cpu("/tmp/2instances/cpu_gci_3K_300KB_5K_0_4.csv"),
  read.cpu("/tmp/2instances/cpu_gci_3K_300KB_5K_1_4.csv"),
  read.cpu("/tmp/2instances/cpu_gci_3K_300KB_5K_0_5.csv"),
  read.cpu("/tmp/2instances/cpu_gci_3K_300KB_5K_1_5.csv")
)
cpu.nogci <- rbind(
  read.cpu("/tmp/2instances/cpu_nogci_3K_300KB_5K_0_1.csv"),
  read.cpu("/tmp/2instances/cpu_nogci_3K_300KB_5K_1_1.csv"),
  read.cpu("/tmp/2instances/cpu_nogci_3K_300KB_5K_0_2.csv"),
  read.cpu("/tmp/2instances/cpu_nogci_3K_300KB_5K_1_2.csv"),
  read.cpu("/tmp/2instances/cpu_nogci_3K_300KB_5K_0_3.csv"),
  read.cpu("/tmp/2instances/cpu_nogci_3K_300KB_5K_1_3.csv"),
  read.cpu("/tmp/2instances/cpu_nogci_3K_300KB_5K_0_4.csv"),
  read.cpu("/tmp/2instances/cpu_nogci_3K_300KB_5K_1_4.csv"),
  read.cpu("/tmp/2instances/cpu_nogci_3K_300KB_5K_0_5.csv"),
  read.cpu("/tmp/2instances/cpu_nogci_3K_300KB_5K_1_5.csv")
)
```
```{r gctrace_overall}
summary(cpu.gci$cpu)
summary(cpu.nogci$cpu)
hist((cpu.gci$cpu/200)*100, breaks=50, main="CPU Usage (GCI On)", xlab="CPU Usage (%)", xlim = c(0, 100))
hist((cpu.nogci$cpu/200)*100, breaks=50, main="CPU Usage (GCI Off)", xlab="CPU Usage (%)", xlim = c(0, 100))
quantile(cpu.gci$cpu, c(0.9,0.99,0.999,0.9999, 0.99999))
quantile(cpu.nogci$cpu, c(0.9,0.99,0.999,0.9999, 0.99999))
```

## Null-Hyphothesis check (around the median)
```{r}
# Non parametric test which checks the pseudo-median
# https://en.wikipedia.org/wiki/Mann%E2%80%93Whitney_U_test
wilcox.test(cpu.gci$cpu, conf.int = TRUE, conf.level = 0.95)
wilcox.test(cpu.nogci$cpu, conf.int = TRUE, conf.level = 0.95)
```

# Appendix

## Commands used to execute the experiment

Note: Using fake IP addresses.

```
$ INSTANCES="1.1.1.1 1.1.1.2" ./update-msgpush.sh 
$ ROUND_START=1 ROUND_END=5 EXPERIMENT_DURATION=80s SUFFIX=_3K_300KB_5K THROUGHPUT=3000 MSG_SIZE=361200 WINDOW_SIZE=5000 USE_GCI=true INSTANCES="1.1.1.1 1.1.1.2 LB=1.1.1.5 ./run-msgpush.sh
$ ROUND_START=1 ROUND_END=5 EXPERIMENT_DURATION=80s SUFFIX=_3K_300KB_5K THROUGHPUT=3000 MSG_SIZE=361200 WINDOW_SIZE=5000 USE_GCI=false INSTANCES="1.1.1.2 1.1.1.2" LB=1.1.1.5 ./run-msgpush.sh
```

## Nginx.conf

Note: Using fake IP addresses.

```
user www-data;
worker_processes auto;
pid /run/nginx.pid;

events {
        worker_connections 768;
        # multi_accept on;
}

http {
        upstream backends {
            server 1.1.1.1:3000 max_fails=0 fail_timeout=15s;
            server 1.1.1.2:3000 max_fails=0 fail_timeout=15s;
            #server 1.1.1.3:3000 max_fails=0 fail_timeout=15s;
            #server 1.1.1.4:3000 max_fails=0 fail_timeout=15s;
        }

        server {
            listen 80;

            location / {
                proxy_pass http://backends;
                proxy_next_upstream  timeout error http_503;
                proxy_next_upstream_tries 0;
                proxy_read_timeout 5m;
            }
        }

        ##
        # Logging Settings
        ##
        log_format exp '$msec;$status;$request_time;$upstream_response_time';
        access_log /var/log/nginx/access.log exp;
        error_log /var/log/nginx/error.log;

        ##
        # Virtual Host Configs
        ##

        #include /etc/nginx/conf.d/*.conf;
        #include /etc/nginx/sites-enabled/*;
}
```