---
title: "GCI-Go reaches the Cloud: Experiments and simulation results"
author: "Daniel Fireman (danielfireman@gmail.com)"
date: "January, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=F)

require(gridExtra)
require(boot)
require(dplyr)
require(stringr)
require(cowplot)

source("functions.R")
```
# Experiment setup

* Throughput: 80
* Threads: 1
* Connections: 2
* Message size (amount of memory allocated per request): 204800
* Experiment duration: 120s
* Instance: 2cores, 1GB RAM

# Simulator Cross-Validation

*Simulator Assumptions*

* Linear Scalability
* Network latency is constant: 1ms

*Hyphotesis*

* $H_{0}$: The simulated latency is different from experimental latency for 1, 2 and 4 instances.

```{r}
al1.exp.gci <- accesslog("1i", "gci", 4)
al1.sim.gci <- rbind(
  read.csv("1i/sim_lb_gci_1.csv"),
  read.csv("1i/sim_lb_gci_2.csv"),
  read.csv("1i/sim_lb_gci_3.csv"),
  read.csv("1i/sim_lb_gci_4.csv"))
```

# Simulation Results



# Appendix

## Simulator

*Inputs*

*Assumptions*

*Output*




